%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% A clean template for an academic CV
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt, a4paper]{article}

\newcommand{\dept}{Department of Earth \& Atmospheric Sciences}
\newcommand{\university}{University of Houston}

% Identifying information
\newcommand{\Title}{Curriculum Vit\ae}
\newcommand{\FirstName}{Xiaolong}
\newcommand{\LastName}{Wei}
\newcommand{\Initials}{X}
\newcommand{\MyName}{\FirstName\ \LastName}
\newcommand{\Wei}{\textbf{\LastName, \Initials.}}  % For citations
\newcommand{\WeiSun}{\textbf{\LastName, \Initials.} and Sun, J.}  % For citations
\newcommand{\Email}{xiaolongw1223@gmail.com}
\newcommand{\Website}{researchgate.net/profile/Xiaolong\_Wei}
\newcommand{\Lab}{https://sites.google.com/view/jiajiasun}
\newcommand{\ORCID}{0000-0002-3160-6086}
\newcommand{\Affiliation}{\dept, \university}
\newcommand{\Address}{
  Room 126, Science \& Research Building 1, 3507 Cullen Blvd, Houston, Texas, USA
}

% Control the font size
\usepackage{anyfontsize}

% For fancy and multipage tables
\usepackage{tabularx}
\usepackage{ltablex}
% Define a new environment to place all CV entries in a 2-column table.
% Left column are the dates, right column the entries.
\usepackage{environ}
\NewEnviron{EntriesTable}{
	\TablePad
	\begin{tabularx}{\textwidth}{@{}p{0.1\textwidth}@{\hspace{0.02\textwidth}}p{0.88\textwidth}@{}}
		\BODY
	\end{tabularx}
}

% Macros to add links
\newcommand{\DOI}[1]{doi:\href{https://doi.org/#1}{#1}}

% Macros to set the year and duration on the left column
\newcommand{\Duration}[2]{\fontsize{10pt}{0}\selectfont #1--#2}
\newcommand{\Year}[1]{\fontsize{10pt}{0}\selectfont #1}
\newcommand{\Future}{future}
\newcommand{\Review}{under review}
\newcommand{\Revision}{under revision}
\newcommand{\Appointment}[4]{\textbf{#1} \newline #2 \newline #3 \newline #4}

% numbering items in reversed orders
\usepackage{etaremune}

% Define command to insert month name and year as date
\usepackage{datetime}
\newdateformat{monthyear}{\monthname[\THEMONTH], \THEYEAR}

% Set the page margins
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}

% Increase the line spacing
\renewcommand{\baselinestretch}{1.1}
% and the spacing between rows in tables
\renewcommand{\arraystretch}{1.5}

% Remove space between items in itemize and enumerate
\usepackage{enumitem}
\setlist{itemsep=0.2em}

% Use custom colors
\usepackage[usenames,dvipsnames]{xcolor}

% Set fonts. Requires compilation with xelatex
\usepackage{fontspec}  % required to make older xelatex compile with UTF8

% Set fancy headers
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\chead{
  \fontsize{10pt}{12pt}\selectfont
  \MyName
  \hspace{0.2cm} -- \hspace{0.2cm}
  \Title
  \hspace{0.2cm} -- \hspace{0.2cm}
  \monthyear\today
}
\rhead{}
\cfoot{\fontsize{10pt}{0}\selectfont \thepage}
\renewcommand{\headrulewidth}{0pt}

% Metadata for the PDF output and control of hyperlinks
\usepackage[colorlinks=true]{hyperref}
\hypersetup{
  pdftitle={\MyName\ - \Title},
  pdfauthor={\MyName},
  linkcolor=blue,
  citecolor=blue,
  filecolor=black,
  urlcolor=MidnightBlue
}

\begin{document}

% No header for the first page
\thispagestyle{empty}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% HEADER
\begin{center}
	{\fontsize{36pt}{0}\selectfont \MyName}
	\\[-0.1cm]
	\rule{\textwidth}{0.6pt}
	\\[0.4cm]
	{\fontsize{10pt}{0}\selectfont
		\Affiliation
		\\[0.1cm]
		\Address
		\\[0.1cm]
		Email: \href{mailto:\Email}{\Email}
		\, | \,
		ORCID: \href{https://orcid.org/\ORCID}{\ORCID}
		\\
		Website: \href{https://www.\Website}{\Website}
	}
\end{center}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}

\begin{EntriesTable}
  \Duration{2018}{}  &
  \textbf{Ph.D in Geophysics}, University of Houston, Houston, USA
  \\
  \Duration{2015}{2018}  &
  \textbf{M.S. in Geology}, Northwest University, Xi'an, China
  \\
  \Duration{2011}{2015}  &
  \textbf{B.S. in Geophysics}, China University of Geosciences, Beijing, China

\end{EntriesTable}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Research Interests}

\begin{itemize}
	\item Inversion of geophysical data sets (e.g., gravity, gravity gradiometry and magnetic data).
	\item Structural similarity constraint joint inversion.
	\item Uncertainty analysis in geophysical separate/joint inversions in both deterministic and stochastic frameworks.
	\item Geology differentiation models.
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Awards \& Honors}

\begin{EntriesTable}
	\Year{2020}  &
	Outstanding Academic Achievement, University of Houston, Houston, USA
	\\
	\Year{2018}  &
	The First Prize Scholarship, Northwest University, Xi'an, China
	\\
	\Year{2017}  &
	The First Prize Scholarship, Northwest University, Xi'an, China
	\\
	\Year{2016}  &
	The First Prize Scholarship, Northwest University, Xi'an, China
	\\
	\Year{2015}  &
	Best Bachelor Thesis, China University of Geosciences, Beijing, China
	\\
	\Year{2013}  &
	The Second Prize Scholarship, China University of Geosciences, Beijing, China


\end{EntriesTable}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Publications}


\subsection{Peer-Reviewed}

\begin{EntriesTable}
	\Year{2020}  &
	\WeiSun, 2020. Uncertainty analysis of 3D potential-ﬁeld deterministic inversion using mixed Lp norms. \emph{Geophysics}. \Revision
	\\
	\Year{2020}  &
	Sun, J., \Wei, 2020. Recovering sparse models in 3D potential‐field inversion without bound dependence or staircasing problems using a mixed Lp‐norm regularization. \emph{Geophysical Prospecting}.
	\DOI{10.1111/1365-2478.13063}.
	\\
	\Year{2020}  &
	Sun, J., Melo, A., Kim, J.D. and \Wei, 2020. Unveiling the 3D undercover structure of a Precambrian intrusive complex by integrating airborne magnetic and gravity gradient data into 3D quasi-geology model building. \emph{Interpretation}, 8(4), pp.1-50.
	\DOI{10.1190/INT-2019-0273.1}.
	\\

\end{EntriesTable}



\subsection{Conference}

\begin{EntriesTable}
	\Year{2020}  &
	\WeiSun, 2020. Uncertainty analysis of joint inversion using mixed Lp-norm regularization. In \emph{SEG Technical Program Expanded Abstracts 2020} (pp. 925-929). Society of Exploration Geophysicists. \DOI{10.1190/segam2020-3428359.1}.
	\\
	\Year{2020}  &
	Sun, J., Melo, A., Deok Kim, J. and \Wei, 2020. Characterizing a Precambrian intrusive complex by integrating potential field data into 3D quasi-geology model building. In \emph{SEG Technical Program Expanded Abstracts 2020} (pp. 1374-1378). Society of Exploration Geophysicists. \DOI{10.1190/segam2020-3428385.1}.
	\\
	\Year{2020}  &
	\WeiSun, 2020. Quantifying uncertainties of deterministic geophysical inversions using mixed Lp norms. In \emph{SEG Technical Program Expanded Abstracts 2020} (pp. 1404-1408). Society of Exploration Geophysicists. \DOI{10.1190/segam2020-3420227.1}.
	\\

\end{EntriesTable}




\end{document}
